\TheTitle

### 2017-07-07 paper/lineval.tex
Mashing the two papers together

\begin{abstract}
\end{abstract}

@@

\section{Introduction}
\label{sec:introduction}

Between 50k and 70k commits are added to the Linux kernel per version
requiring maintainers of older versions of the kernel to sift through
thousands of commits and merges with tools that are unable to filter and
effectively visualize projects at the scale of the kernel. Older
versions of the kernel are used in embedded systems and mobile phones;
for security purposes, performance needs, and changing hardware
requirements, maintainers must be able to understand the changes being
made in the current version of the kernel in order to produce the
necessary patches for the older versions of the kernel. Current tools
and visualizations are based on the directed acyclic graph (DAG) of the
repository, showing all commits and merges in chronological order by
when the commit was authored, not by when it arrived in the official
Linux repository.

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/gitk.png}
  \caption{
    The Gitk interface, centered at commit
    cdbdd1676a5379f1d5cbd4d476f5e349f445befe. The top left pane showing
    the DAG, the top center pane showing the authors, and top right pane
    showing the commit dates. The bottom-left pane shows the full
    commit message and diff of the selected commit, and the bottom-right
    pane shows the list of the files modified by the selected commit.
  }
  \label{fig:gitk}
  %\vspace{-4mm}
\end{figure}

Git is a distributed version control system that is used in many
open-source and closed-source projects. Git enables many developers to
write code simultaneously, working on various components known as
branches. Git uses a directed acyclic graph model (DAG) for storing the
necessary information regarding the state of the code at any point in
time. Git refers to nodes of the DAG as commits, not distinguishing
between the code-carrying commits and the structural commits that bring
two branches together. In this paper, we will refer to the individual
commits as being commits, the structural merge commits as merges, and
refereeing to all as repository events.

The DAG representation works in smaller projects; it enables users to
see when changes are made, when these changes are merged, how each
branch is interacting, and the point where a branch forks from the
master branch. In large modular projects, like the Linux kernel, the DAG
becomes a mess of merges and commits (Figure~\ref{fig:gitk}) losing its
visual meaning. In some cases, the repository is simply too large for
systems to generate a visualization; repositories stored on GitHub will
have a DAG visualization to show the branches and forks of a
repository, but is unable to display the visualization for projects at
the scale of Linux or even the Git Git
repository(Figure~\ref{fig:gitfail}). Between 60k and 70k new commits
are created for the Linux project every year; according to previous
work\cite{German2015}, a commit takes a median of 30 days from the time
it is authored until it arrives in the official repository. The snapshot
of the kernel tomorrow may be different than the snapshot from today,
containing new commits authored in the past; distinguishing these new
commits from the commits in the snapshot from today is not trivial.

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/github_viewer.png}
  \caption{Github is unable to display the DAG of the Linux
    Project due to the size and complexity, which would normally
    show the relationship to other branches and forks.}
  \label{fig:gitfail}
  %\vspace{-2mm}
\end{figure}

@@

\section{\mt Model}
\label{sec:mt_model}

We propose a new model, built from the DAG, with the purpose of
providing a clearer conceptual image of how a commit is merged, other
commits that are merged with a commit, and a summarization of the entire
group of commits that are merged with a commit. We call our model the
\mt model. The model inverts the DAG, so that reference point from
parent to child instead of from child to parent. This enables the
aggregation of commit metrics at merges. Given a merge, we are able to
recursively traverse the children of the merge, collecting the
statistics at each commit. The commits become the leaves of the tree,
and internal nodes are merges that do not merge into the master branch
of the repository. We terminate the further traversal of an edge under
two conditions; first, if the next event is on the master branch of the
repository, second, if the next event has a shorter path into the master
branch of the repository. As a consequence, commits will always take the
shortest path, in terms of commit time, to the master branch.

A short example: assume the commits represented in
Figure~\ref{fig:repoEvents} show the sequence of events in a repository.
In this case, commits are performed in various repositories and
branches. The DAG representation of the commits is shown in
Figure~\ref{fig:repoDAG}. Notice that the DAG loses information about
the master branch and the repository that the master branch is part of.
The \mt view of this DAG is visible in Figure~\ref{fig:repoTree}.
Note that the direction of the edges of the DAG have been inverted,
instead of pointing from the child to the ancestors, it points from the
ancestor to its successors, forming a path to the master branch. Also
note that the DAG has been simplified, showing only a single edge on the
path to master for any commit.

@@

\begin{figure}[htbp]
  \centering
  \begin{tikzpicture}[auto, on grid, semithick, state/.style={circle, text=black}]
    \node[state] (1) {1};
    \node[state, above right= of 1] (2) {2};
    \node[state, above right= 2cm and 1cm of 2] (3) {3};
    \node[state, right= 2cm of 1] (4) {4};
    \node[state, above right=of 4] (5) {5};
    \node[state, above right=of 5] (6) {6};
    \node[state, right=of 5] (7) {7};
    \node[state, above right= 2cm and 1cm of 7](8) {8};
    \node[state, right= 2cm of 7] (9) {9};
    \node[state, right=of 9] (10) {10};
    \node[state, below right=of 9] (11) {11};
    \node[state, below right=of 10] (12) {12};

    \draw (12) edge[-stealth] (11) edge[-stealth] (10);
    \draw (11) edge[-stealth] (4) edge[-stealth] (9);
    \draw (10) edge[-stealth] (9);
    \draw (9) edge[-stealth] (8) edge[-stealth] (6)
              edge[-stealth] (7);
    \draw (8) edge[-stealth] (7);
    \draw (7) edge[-stealth] (5);
    \draw (6) edge[-stealth] (5);
    \draw (5) edge[-stealth] (3) edge[-stealth] (2)
              edge[-stealth] (4);
    \draw (4) edge[-stealth] (1);
    \draw (3) edge[-stealth] (2);
    \draw (2) edge[-stealth] (1);
  \end{tikzpicture}
  \caption{DAG representation of the commits represented in
    Figure~\ref{fig:repoEvents}. The DAG does not maintain the
    information about which repository a commit comes from. Furthermore,
    the DAG does not distinguish the master branch from other branches.}
  \label{fig:repoDAG}
\vspace{-3mm}
\end{figure}

@@

  \end{tikzpicture}
  \caption{\mt view of the commits  represented in
    Figure~\ref{fig:repoEvents} showing the path they followed to reach
    the master branch. In this model the successors of each commit
    represents the path followed by that commit to reach the master
    branch.}
  \label{fig:repoTree}
\vspace{-3mm}
\end{figure}

Computing the \mt from a DAG for any repository may not be
possible; however, certain features of the development process of Linux
make it feasible to compute the \mt for the Linux repository.
First, the master branch of Linux is maintained by Linus Torvalds, and
only Linus has write access to it. We have verified this assertion in
previous research~\cite{German2015}. We have developed a heuristic that
is presented in Algorithm~\ref{fig:alg}. In short, the algorithm first
identifies the commits made directly to the master branch; whereafter it
recursively determines the shortest path (in terms of time), using the
DAG, from each commit to the master branch using the inverted DAG.

\begin{algorithm}
        \caption{Computing the \mt from Linux Git's DAG}\label{fig:alg}
        \label{alg:original}
        \begin{algorithmic}
                \Function{ComputeMergeTree}{DAG}: tree
                \State {\# Compute the tree from the DAG of Linux repository.}
                \State {\# Returns $Tree$, a graph containing every commit }
                \State {\# in DAG with the path it followed to master.}

@@

We evaluate the performance of the heuristic using the merge log made by
Linus Torvalds, the original creator of Linux, and primary merger of all
other repository events into the master branch of the repository. In
Figure~\ref{fig:sampleMerge}, we see an example of the merge log.

@@

* 'for-linus' of git://neil.brown.name/md: (24 commits)
md: clean up do_md_stop
[... edited for the sake of space]
md: split out md_rdev_init
md: be more careful setting MD_CHANGE_CLEAN
md/raid5: ensure we create a unique name for kmem_cache...
...
    \end{verbatim}}\vspace{-5mm}
  \caption{Example of how merges record a subset of commits being
    merged. The commit only shows the first 20 one-line summaries
    messages for the 24 non-merge commits it merged. The ending
    ``\ldots'' is part of the log and represents that other
    commits were merged.}
  \label{fig:sampleMerge}
\end{figure}

We use this information to evaluate the accuracy of the \mt model
extracted from the DAG\@. The method we followed started with the
extraction of the commit history up to July 20, 2016. We computed the
merge tree of every commit until then. Since Linus Torvalds mostly does
merging directly into master, we assumed that every merge by him is the
root of a \mt. As described above, the log of a merge-commit usually
contains the number of commits in the merge the first 20 summaries of
commits being merged. We extracted merges by Linus Torvalds using the
command \mycode{log --merges --author='Torvalds} and compared the number
of commits according to the log with the number of commits in the  \mt
rooted in this commit. We also used the summaries of the commits found
in the merge (not necessarily all---see above) to make sure those
commits were in their corresponding merge tree. For example, for the
merge in Figure~\ref{fig:sampleMerge} we would expect that the merge
tree rooted at \mycode{8cbd84f} contains 24 commits, and the one-line
summaries corresponds to commits in that \mt. We also inspected those
with differences to make sure they were true errors.  The results can be
summarized as follows:

    Five merges were false-errors because their logs did not contain
    accurate information (were probably edited by hand). For example in
    \mycode{42a579a0f\ldots} one commit summary was missing (the line was
    empty), in \mycode {c55d267\ldots} the summaries were reordered.

    The heuristic correctly identified that 79 of Linus merges (between
    Jun 7, 2014 and Jun 2, 2014) were made to a branch (not master).
    This branch was merged at \mycode{3f17ea6d\ldots} which contained 6809
    commits.

    The heuristic worked perfectly until Sept 4, 2007, the earliest date
    that it could be verified.  Before this date, and until Dec 12,
    2006, merges did not include a summary of the commits they included,
    hence making it impossible to verify; during this period, however,
    we correctly identified the merges by Linus into master.

    Before Dec. 12, 2006 (1542 merges) our heuristic breaks due to the
    presence of a \textit{foxtrot} commit (\mycode{c436688\ldots}),
    which confounded the true master branch of a repository (see
    \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html}
    for a description of the issue).

In summary, of the merges after Sept. 4, 2007, our heuristic was correct
in 100\% of the 16,680 commits. It failed in 1,542 commits before Dec.
12, 2006 and in 836 it appears to be correct (Dec 7, 2006 to Sept 4,
2007).

\section{Design and Implementation}
\label{sec:design_and_implementation}

We implement a tool, \tool, to test and verify the capabilities of the
\mt model. \tool provides search, summarization, and
visualization using the \mt model.

We provide users with search-based navigation. The search engine takes a
plain text query from the user and returns results based on similarity
to the query. The engine weighs various fields, including the commit
log, the author name, the commit hash, and the dates that the commit was
authored and committed. The results are aggregated by the \mt
with a link to the root at the top, and the repository events that match
the search query in a table below.  An example of a single \mt is shown
in Figure~\ref{fig:linvis_search_results}.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=1.0\linewidth]{figures/linvis/search_results.png}
  \caption{\tool search results for `net-next 2011', showing a single
    \mt group.}
  \label{fig:linvis_search_results}
\end{figure}

\tool uses seven tabs to show the information and visualizations for a
selected commit or merge. The message tab shows the full commit log
message. This does not include the diff. The files tab shows an
aggregated table of all files that were modified in a merge. It includes
metrics like the number of lines added, lines removed, total lines
modified, and the delta, summed across all commits in the merge tree
that modify this file. A small details drop-down button allows a user to
see exactly which commit makes the changes, as shown in
Figure~\ref{fig:linvis_files}. If the current repository event being
viewed is a commit, the aggregate views will only show modifications
made by the commit. The modules tab shows the modules modified in the
merge tree. Like the files tab, the modules tab uses a table to show the
name of the module, the number of commits that are in the merge tree
that work with the module, and a details button to provide the links to
those commits.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=1.0\linewidth]{figures/linvis/linvis_files.png}
  \caption{Table showing the modified files in a merge, with the second
  entry expanded to show the commit that makes the changes.}
  \label{fig:linvis_files}
\end{figure}

The authorship tab is very similar to the files tab, but shows the
authorship information. It shows the sum of the number of lines added,
removed, modified, and the delta within the \mt. It also shows
the number of files that were modified by the author. The details tab is
organized slightly differently. Instead of organizing these results by
commit, the details are organized by file, showing which files were
modified by the author in this \mt (Figure~\ref{fig:linvis_authors}).

\begin{figure}[htpb]
  \centering
  \includegraphics[width=1.0\linewidth]{figures/linvis/linvis_authors.png}
  \caption{Table showing the authors who made changes in a merge. The
    entry for Randy Dunlap is expanded, showing the modifications to
    each file that were made by Randy.}
  \label{fig:linvis_authors}
\end{figure}

\tool implements three visualizations, a list tree, pack tree, and
Reingold-Tilford tree. The list tree is a series of indented textual
lists that can be easily searched with the built-in search in most
web-browsers. The list tree is rooted at the current event, if the event
is a commit, only that commit will be shown; conversely, if the selected
event is the root, the entire merge tree will be shown. The Pack-Tree or
Bubble tree, uses a set-based approach for showing the parent
relationship. The root node aggregates all of the events within the \mt
into the master branch. Thus, the root is the superset of all the other
nodes in the tree. The commits are shown as individual white circles,
containing no other events, as these are the leaves. This is shown in
Figure~\ref{fig:linvis_pack}. The selected event will be shown in bright
orange, commits in white, and merges in shades of blue. Darker shades of
blue indicate that the merge is deeper in the tree.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/linvis/linvis_bubble.pdf}
  \caption{The pack tree visualization for a selected commit, shown in
    orange.}
  \label{fig:linvis_pack}
\end{figure}

The Reingold-Tilford tree is the classic tree visualization, with the
root at the top, leaves at the bottom, and the edges between them
showing the parent relationship. An example of the Reingold-Tilford tree
visualization is shown in Figure~\ref{fig:commit_1} and
Figure~\ref{fig:commit_2}.

>>>>

\begin{abstract}

  With an average of more than 900 top-level merges into the Linux
  kernel per release, many containing hundreds of commits and some
  containing thousands, maintenance of older versions of the kernel
  becomes nearly impossible.  Various commercial products, such as the
  Android platform, run older versions of the kernel. Due to security,
  performance, and changing hardware needs, maintainers must understand
  what changes (commits) are added to the current version of the kernel
  since the last time they inspected it in order to make the necessary
  patches.

  Current tools provide information about repositories through the
  directed acyclic graph (DAG) of the repository, which is helpful for
  smaller projects. However, with the scale and number of branches in
  the kernel the DAG becomes overwhelming very quickly. Furthermore, the
  DAG contains every ancestor of every commit, while maintainers are
  more interested in how and when a commit arrives to the official Linux
  repository.

  In this paper, we propose the merge-tree, a simplified transformation
  of the DAG of the Linux git repository that shows the way in which
  commits are merged into the master branch of Linux. Using the
  merge-tree, we build \tool, a tool that is designed to allow users to
  explore how commits are merged into the Linux kernel.

\end{abstract}

@@

\section{Introduction}

Between 50k and 70k commits are added to the Linux kernel per version
requiring maintainers of older versions of the kernel to sift through
thousands of commits and merges with tools that are unable to filter and
effectively visualize projects at the scale of the kernel. Older
versions of the kernel are used in embedded systems and mobile phones;
for security purposes, performance needs, and changing hardware
requirements, maintainers must be able to understand the changes being
made in the current version of the kernel in order to produce the
necessary patches for the older versions of the kernel. Tools like Gitk
use a directed acyclic graph (DAG) model of the repository, showing all
commits and merges in chronological order by when the commit was
authored, not by when it arrived in the official Linux repository.

\begin{figure*}
        \centering
        \includegraphics[width=0.97\textwidth]{figures/gitk.png}
        \caption{A view of the Gitk interface centered on merge
          b34870fc9ff15fe46c4066faeeec437a4e63e2d8 by Miller. Commits point toward
          their ancestors and there is no clear path from the commit to the merge
          with the master branch. Neither Gitk nor Git are capable of showing the
          commits in master.}
        \label{fig:gitk}
%\vspace{-4mm}
\end{figure*}

\begin{figure}
        \centering
        \includegraphics[width=0.45\textwidth]{figures/github_viewer.png}
        \caption{Github Failure Message showing the DAG of the Linux Project and its
                relationship to other forks.}
        \label{fig:gitfail}
%\vspace{-2mm}
\end{figure}

This representation works in smaller projects; it enables users to see
when changes are made, when these changes are merged, how each branch is
interacting, and the point where a branch forks from the master branch.
In large modular projects, like the Linux kernel, the DAG becomes a mess
of merges and commits (Figure~\ref{fig:gitk}) losing its visual meaning.
In some cases, the Linux kernel is simply too large for the system to
generate a visualization; Github provides a DAG view for many projects,
but is unable to display the visualization for projects at the scale of
the Linux of the kernel (Figure~\ref{fig:gitfail}).  Between 60k and 70k
new commits are created for the Linux project every year; according to
our previous work\cite{German2015}, a commit takes a median of 30 days
from the time it is authored until it arrives in the official
repository. The snapshot of the kernel tomorrow may be different than
the snapshot from today, containing new commits authored in the past;
distinguishing these new commits from the commits in the snapshot from
today is not trivial.

@@

\section{Merge-Tree model}
\label{sec:mergetree}

Git uses a directed acyclic graph (DAG) as its main data model. In this
model, a commit has one or more ordered parents (ancestors), except the
root commits of a repository which do not have ancestors--Linux's git
repository has two such commits.  Commits are divided into merge
commits, merging two or more branches, and non-merge commits. Non-merge
commits have only one parent, while merge commits have two or more. The
order of the parents matter: the first parent is the branch in which the
merge is being done, while the rest indicate the branches being merged
(Git allows merging multiple branches simultaneously). The second parent
is the first branch merged, the third parent is the second branched
merged, etc.

Once a commit is created, it is never changed. Git allows operations to
alter commits or reorder them, but it changes the commit ID in the
process, effectively replacing it with a new commit. This makes commits
unable to record the traversal of merges from the commit to the merge
into the master branch.

A short example: assume the commits represented in
Figure~\ref{fig:repoEvents} show the sequence of events in a repository.
In this case, commits are performed in various repositories and
branches. The DAG representation of the commits is shown in
Figure~\ref{fig:repoDAG}. Notice that the DAG loses information about
the master branch and the repository that the master branch is part of.
The merge-tree view of this DAG is visible in Figure~\ref{fig:repoTree}.
Note that the direction of the edges of the DAG have been inverted,
instead of pointing from the child to the ancestors, it points from the
ancestor to its successors, forming a path to the master branch. Also
note that the DAG has been simplified, showing only a single edge on the
path to master for any commit.

@@

\begin{figure}[htbp]
  \centering
  \begin{tikzpicture}[auto, on grid, semithick, state/.style={circle, text=black}]
    \node[state, draw=chartblue] (1) {1};
    \node[state, draw=chartyellow, above right= of 1] (2) {2};
    \node[state, draw=chartmagenta, above right= 2cm and 1cm of 2] (3) {3};
    \node[state, draw=chartblue, right= 2cm of 1] (4) {4};
    \node[state, draw=chartyellow, above right=of 4] (5) {5};
    \node[state, draw=chartred, above right=of 5] (6) {6};
    \node[state, draw=chartyellow, right=of 5] (7) {7};
    \node[state, draw=chartmagenta, above right= 2cm and 1cm of 7](8) {8};
    \node[state, draw=chartyellow, right= 2cm of 7] (9) {9};
    \node[state, draw=chartyellow, right=of 9] (10) {10};
    \node[state, draw=chartblue, below right=of 9] (11) {11};
    \node[state, draw=chartblue, below right=of 10] (12) {12};

    \draw (12) edge[-stealth] (11) edge[chartyellow, -stealth] (10);
    \draw (11) edge[-stealth] (4) edge[chartyellow, -stealth] (9);
    \draw (10) edge[chartyellow, -stealth] (9);
    \draw (9) edge[chartmagenta, -stealth] (8) edge[chartred, -stealth] (6)
              edge[chartyellow, -stealth] (7);
    \draw (8) edge[chartmagenta, -stealth] (7);
    \draw (7) edge[chartyellow, -stealth] (5);
    \draw (6) edge[chartred, -stealth] (5);
    \draw (5) edge[chartmagenta, -stealth] (3) edge[chartyellow,-stealth] (2)
              edge[chartyellow, -stealth] (4);
    \draw (4) edge[-stealth] (1);
    \draw (3) edge[chartmagenta, -stealth] (2);
    \draw (2) edge[chartyellow, -stealth] (1);
  \end{tikzpicture}
  \caption{DAG representation of the commits represented in
    Figure~\ref{fig:repoEvents}. The DAG loses information about which
    repository the commit is performed in and through which merges it
    has passed on its way to the master branch. The DAG does not even
    distinguish the master branch from other branches.}
  \label{fig:repoDAG}
%\vspace{-3mm}
\end{figure}

@@

  \end{tikzpicture}
  \caption{Merge-tree view of the commits  represented in
    Figure~\ref{fig:repoEvents} showing the path they followed to reach
    the master branch. In this model the successors of each commit
    represents the path followed by that commit to reach the master
    branch.}
  \label{fig:repoTree}
\vspace{-3mm}
\end{figure}

\subsection{Computing the merge-tree of the DAG of Linux}

Computing the merge-tree from a DAG for any repository may not be
possible; however, certain features of the development process of Linux
make it feasible to compute the merge-tree for the Linux repository.
First, the master branch of Linux is maintained by Linus Torvalds, and
only Linus has write access to it. We have verified this assertion in
previous research~\cite{German2015}. We have developed a heuristic that
is presented in Algorithm~\ref{fig:alg}. In short, the algorithm first
identifies the commits made directly to the master branch; whereafter it
recursively determines the shortest path (in terms of time), using the
DAG, from each commit to the master branch using the inverted DAG.

\begin{algorithm}
        \caption{Computing the merge-tree of Linux Git's DAG}\label{fig:alg}
        \begin{algorithmic}
                \Function{ComputeMergeTree}{DAG}: tree
                \State {\# Compute the tree from the DAG of Linux repository.}
                \State {\# Returns $Tree$, a graph containing every commit }
                \State {\# in DAG with the path it followed to master.}

@@

\subsection{Evaluation}

Merges that do not have conflicts provide information to verify this
heuristic. If a merge does not contain a conflict, it records a summary
of the commits that it merges. See Figure~\ref{fig:sampleMerge} for an
example. This summary contains a list of the first 20 non-merge commits
in the merge, including their one-line log description, the full logs of
the merge commits that merge this subset, and the total number of
non-merge commits in the merge.

@@

* 'for-linus' of git://neil.brown.name/md: (24 commits)
md: clean up do_md_stop
[... edited for the sake of space]
md: split out md_rdev_init
md: be more careful setting MD_CHANGE_CLEAN
md/raid5: ensure we create a unique name for kmem_cache...
...
        \end{verbatim}}\vspace{-5mm}
        \caption{Example of how merges record a subset of commits being merged. The
                commit only shows the first 20 one-line summaries messages for the 24
                non-merge commits it merged. The ending ``...'' is part of the log
                and represents that other commits were merged.}
        \label{fig:sampleMerge}
\end{figure}

We used this information to evaluate the accuracy of the merge-tree
model extracted from the DAG. The method we followed started with the
extraction of the commit history up to July 20, 2016. We computed the
merge tree of every commit until then. Since Linus Torvalds mostly does
merging directly into master, we assumed that every merge by him is the
root of a merge-tree. As described above, the log of a merge-commit
usually contains the number of commits in the merge the first 20
summaries of commits being merged. We extracted merges by Linus Torvalds
using the command \mycode{log --merges --author='Torvalds} and compared
the number of commits according to the log with the number of commits in
the  merge-tree rooted in this commit. We also used the summaries of the
commits found in the merge (not necessarily all---see above) to make
sure those commits were in their corresponding merge tree. For example,
for the merge in Figure~\ref{fig:sampleMerge} we would expect that the
merge tree rooted at \mycode{8cbd84f} contains 24 commits, and the
one-line summaries corresponds to commits in that merge-tree. We also
inspected those with differences to make sure they were true errors.
The results can be summarized as follows:

\begin{itemize}
\item Five merges were false-errors because their logs did not contain accurate information (were probably edited by
  hand). For example in \mycode{42a579a0f...} one commit summary was missing (the line was empty), in \mycode
  {c55d267} the summaries were reordered.
\item The heuristic correctly identified that 79 of Linus merges (between Jun 7, 2014 and Jun 2, 2014) were made to a
  branch (not master). This branch was merged at \mycode{3f17ea6d..} which contained 6809 commits.
\item The heuristic worked perfectly until Sept 4, 2007, the earliest date that it could be verified.
  Before this date, and until Dec 12, 2006, merges did not include a summary of the commits they included, hence making it
  impossible to verify; during this period, however, we correctly identified the merges by Linus into master.
\item Before Dec. 12, 2006 (1542 merges) our heuristic breaks due to the
presence of a \textit{foxtrot} commit (\mycode{c436688...}), which confounded the true master branch of a
repository (see \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a description of the issue).
\end{itemize}

In summary, of the merges after Sept 4, 2007, in 100\% of them (16,860)
our heuristic was correct. It failed in 1,542 commits before Dec. 12,
2006 and in 836 it appears to be correct (Dec 7, 2006 to Sept 4, 2007).

\section{Visualizing the merge-tree of Linux}

The goal of \tool is to simplify the navigation of the kernel commit
information, specifically focusing on merges. This is done by leveraging
the merge-tree to inspect how commits are merged on the path to the
master repository.

\subsection{Use cases}

We designed \tool with two use-cases in mind, though a user may switch
between the cases as they work.

\noindent \textbf{Use-case 1: top-to-bottom
  approach}\label{sec:usecase1}\\ These are users that are maintaining a
section of the kernel and would like to pick a merge (including all the
commits that it merges) and merge it directly into their current
repository. This is useful for reducing the amount of re-implementation
work. For these users, it is important to have the ability to aggregate
metadata about files and modules being effected by the merge. Also, it
is important for these users to be able to navigate from the root of the
merge-tree toward the leaves.

\noindent \textbf{Use-case 2: bottom-to-top
  approach}\label{sec:usecase2}\\ These are users that start with a
known merge or commit and would like to see what other changes are being
made in commits that are in the same merge, including knowing the
merge-tree they belong to. This is useful to see what other commits are
related to the current commit and how they get collated into merges that
eventually end in the master branch. This is primarily for maintainers
that need to perform some specific cherry picking of commits. We must
provide these users a mechanism for navigating from a single commit
toward the master branch, allowing them to see other commits that might
be related to their original commit.

\subsection{Data Model}

In our visualizations, we leverage the merge-tree model described in
Section~\ref{sec:mergetree}. In this model each commit is either already
in the master branch, or is part of a tree which is rooted in the merge
that merged it into the master branch.  Each commit, whether a merge or
non-merge, has only one successor; the root of each tree has none as it
was made by Linus Torvalds directly into the master branch. Non-merge
commits contain the metadata for the changes made.  This metadata
includes the files changed, the lines added and removed from each file,
the author, the date the commit was merged into the merge that led to
being merged into the kernel, the date the commit was authored, the
patch, and the commit log. Merges contain less metadata, only storing
the author of the merge, the log, the commit date, and the author date,
and potentially, changes necessary to address conflicts during the
merge. The details of the model are outlined in \cite{German2015}.

\section{Design and Implementation}

To navigate and inspect the merge-tree view of the kernel we created a
web-based tool called \tool. Creating a web-based tool enables users to
use the system without having to install additional software or store a
large database, making it more accessible, more easily maintainable, and
platform independent. \tool uses the following mechanisms to reach our
goals of better navigation and better explanation of the selected
changes.

\begin{itemize}
        \item Filter by searching
        \item View files edited
        \item View modules
        \item Tree viewer
\end{itemize}

\subsection{Searching}

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/search.png}
        \caption{Search View allows filtering commits that were merged in a given
                period, filtering by author, keyword, or commit ID.}
        \label{fig:search}
\end{figure}

Searching (depicted in Figure \ref{fig:search}) allows a user to filter
commits and merges that are irrelevant. The search mechanism breaks down
the results by release version. A user can further narrow down the
search by specifying a range of dates in which such commits were merged
by Linus into the master branch---not when the commits were created
(author date and/or commit date). This distinction is important. We have
observed commits that have taken years to arrive into the master
repository after they were originally created.

A user may then provide a search text, filtering by the author name, the
commit ID, or keyword from the log. Any part of the author name may show
up in the results, including searching by email address.

If the user is searching by commit ID, the ID can be specified by using
any of its unique prefixes. For example, the commit
\mycode{3f17ea6dea8ba5668873afa54628a91aaa3fb1c0} is returned when the
user searches for a commit ID of \mycode{3f17e} in the 3.16 Linux
kernel.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/search_results_2.png}
        \caption{Search Results. Each table entry is a commit merged in the desired
                merged window.}
        \label{fig:results}
\end{figure}

In the search results (seen in Figure~\ref{fig:results}), the user is
presented with the one-line log message preview, the author's name and
email, the date the commit was authored, and the date the commit was
last committed.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/log_view.png}
        \caption{Panel showing the Commit Message of a commit.}
        \label{fig:message}
\end{figure}

Once a user selects a commit or merge to investigate, they are presented
with a tabbed pane allowing them to view the full commit log, the files
edited, the modules involved, and the merge-tree view.

The first tab displays the full commit log (Figure~\ref{fig:message}).
From this, a user is able to see what they would see had they searched
for the commit using Git log. This doesn't provide additional
information to the other tools, but helps to complete the functionality
of \tool. The commit log provides a user with the information about the
content of the commit and who has signed-off on the commit to ensure
that it is of good quality. The message for merges may contain a summary
of the commits being merged.  The information within these messages is
highly variable, and is completely dependent on the author's style. As
the user moves toward the root-level merge, the quality of these
messages generally improves.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/files_view_2.png}
        \caption{Panel showing the files modified by all the commits that are part
                of this merge.}
        \label{fig:files}
\end{figure}

The second tab is the files tab (Figure~\ref{fig:files}). This tab
provides information on what files have been edited, how many lines were
added, and how many lines were removed in a given commit. For
non-merges, this functionality is similar to the other tools available.
Our tree-based design model allows us to extend this functionality to
merges by aggregating information about all the commits that are
children of the merge in the merge-tree, which other tools are unable to
show. To find the number of lines added to a file in a merge, we take
the sum of the lines added to that file in each of the children of that
merge. We do the same for calculating the number of lines removed.

% This could be extended to use the patch information to determine when a line has been
% replaced rather than incrementing the lines added and removed.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/modules_view_2.png}
        \caption{Panel showing the modules changed by all the commits in this merge.}
        \label{fig:modules}
\end{figure}

The modules tab (Figure~\ref{fig:modules}) shows the modules that are
contained within the commit. Modules are not natively recognized by Git,
and are not going to be present in all repositories. In the Linux
repository, authors put the module they are working on in the one-line
summary of the log-message; for example: the log \emph{gcov: add support
  for FCC 4.9} has updated the \emph{gcov} module (the coverage testing
tool of the kernel). We heuristically extract the module by taking all
text in the log summary of commits until the first colon.  Modules are
logical partitions of the information in the kernel. Depending on where
the author was working, modules can be general, such as ``bluetooth''
and ``wireless'', or can be quite specific for individual hardware, such
as ``ath9k\_hw'' and ``wl1251''. In a few cases, the author of a commit
does not correctly follow this format and the heuristic approach fails.
As with the Files panel, non-merge commits show their corresponding
information, but for merge commits we aggregate all the modules changed
in all the commits that are part of that merge.  The output of this view
is shown in Figure~\ref{fig:modules}.

Finally, we have the Tree view tab. The tree view is designed for
providing easy navigation of the commits within the merge-tree that is
rooted in the current merge.  It also provides a clear topological view
of the merge and the submerges it includes. We have experimented with
various tree designs to find a design that allows for easy navigation
and visualization of both large and small trees. We discuss this panel
in the next subsection.

\subsection{Merge-Tree Views} \label{treeview_section}

The merge-tree view is what makes \tool unique to other tools that
inspect the DAG of a Git repository. With it, a user can inspect how
commits are merged on their way to the master branch. We have
experimented with various types of trees:

\begin{enumerate}
        \item List trees are a text-based representation of the merge-tree, and are easy to search and navigate.
        \item Reingold-Tilford trees provide a clear visual representation of the tree structure of the merge-tree.
        \item Bubble trees organize the data hierarchically by having the parent node contain the child nodes similarly to tree maps, but
                clearly showing the parent-child relationships between commits and merges.
\end{enumerate}

\subsubsection{List Tree}

The list tree viewer (Figure~\ref{fig:list_tree}) is in the form of
nested lists, and is designed to more closely model the tree view found
in file browsers. This tree only contains the commits and merges that
are within the subtrees of the current merge. A commit will never have
any items in this tree as it is a leaf. To accompany the tree, we
include breadcrumbs at the top of the page to enable a user to navigate
both from the root to the leaves and from a leaf to the root. The last
item in the breadcrumb list is the current commit, the previous item is
the parent of the current commit, and the first item is the root merge
into the kernel.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/list_tree.png}
        \caption{List tree view of merge 3f17ea6}
        \label{fig:list_tree}
\end{figure}

\subsubsection{Reingold-Tilford Tree}

The Reingold-Tilford tree\cite{Reingold1981} (Figures
\ref{fig:reingold_tree} and \ref{fig:reingold_tree_zoom}) allows the
visualization and navigation of the entire merge-tree in an intuitive
representation of the tree.  This illustrates a clear notion of root and
leaves, and how to navigate in either direction. Some merge trees are
very large, containing thousands of commits and merged. While the tree
is capable of producing a visualization, it becomes far more difficult
to understand. For example, the merge, 3f17ea6 performed by Linus
Torvalds June 8 2014, contains 7217 commits and merges. \footnote{This
  commit can be inspected at
  \url{http://li.turingmachine/org/commits/3f17ea6dea8ba5668873afa54628a91aaa3fb1c0}}

      \begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/4dc4_tree.pdf}
        \caption{Merge 4dc4226 is a subtree of 3f17ea6, for the power-management
          module of the kernel}
        \label{fig:reingold_tree}
      \end{figure}

      \begin{figure*}
        \centering
        \includegraphics[width=0.98\textwidth]{figures/4dc4_zoom_tree.pdf}
        \caption{Zoomed out view of the Reingold-Tilford tree for merge 4dc4226}
        \label{fig:reingold_tree_zoom}
      \end{figure*}

      The user is initially greeted with their current node centered on
      the screen.  They are able to zoom the tree by scrolling the
      mouse, and clicking and dragging to pan the tree. They can see
      more details about a node by clicking on it, which will provide
      them a link to the specific page for that commit.

\subsubsection{Bubble Tree}

Bubble trees are useful for providing a clear visualization of wide,
hierarchical data\cite{Boardman2000}. The tree structure is represented
by the nesting of nodes; the largest circle is the root, containing all
the other nodes. The smallest circles do not contain any nodes and
therefore represent the leaf nodes.
